Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
Simplify a footnote

If we have evidence that does not fit into the user documentation, but
would rather be part of a design document, we use Hspec\footnote{%
Hspec was originally implemented by Trystan Spangler, and is now
maintained and actively/further developed by one of the authors.}.

>>>>

If we have evidence that does not fit into the user documentation, but
would rather be part of a design document, we use Hspec\footnote{%
Hspec was originally implemented by Trystan Spangler, and is now
maintained by one of the authors.}.
